Elders PM Summary

### 2020-08-24 dustrak_data_cleaning.Rmd
PM and RH cleaning/summary

# Change function input to look at specific home
# Run these 4 lines together
pm_time_plot_function(location = "NPT", id = "52", visit = 1)
head(gaps, 10)
head(pm_desc, 10)
tail(pm_desc, 10)

@@

elders_pm_new <- elders_pm %>% 
  mutate(pm = if_else(pm > 12000, 999999, pm)) %>% 
  replace_with_na(replace = list(pm = 999999)) %>% 
  # join with file on data cleaning notes - refer to pm_sample_times_comparison file
  left_join(pm_sample_times_comparison, c("area", "home", "home_winter_id", "winter_id", "sampling_visit")) %>% 
  # filter out sampling visits with bad data - refer to pm_sample_times_comparison file
  filter(next_steps != "Do not use due to short run time") %>% 
  filter(next_steps != "Do not use due to high baseline/minimum values") %>% 
  filter(next_steps != "Do not use due to negatives") %>% 
  # replace PM < 1 (lower DustTrak limit) with 0.5 (lower limit / 2) 
  # only doing this for files with a few negative values
  mutate(pm = if_else(pm < 1, 0.5, pm)) %>% 
  # fix files with incorrect datetimes 
  mutate(datetime_pm = ymd_hms(datetime_pm),
         pm_datetime_new = if_else(next_steps == "Subtract 1 hour from datetime", 
                                   datetime_pm - 3600, datetime_pm),
         pm_datetime_new = if_else(next_steps == "Add 1 hour to datetime", 
                                   datetime_pm + 3600, pm_datetime_new),
         pm_datetime_new = if_else(next_steps == "Add 1 day to datetime", 
                                   datetime_pm + 86400, pm_datetime_new),
         pm_datetime_new = if_else(next_steps == "Add 2 hours to datetime", 
                                   datetime_pm + 7200, pm_datetime_new),
         pm_datetime_new = if_else(next_steps == "Add 174970 hours to datetime", 
                                   datetime_pm + 629892000, pm_datetime_new),
         pm_datetime_new = if_else(next_steps == "Subtract 2 hours from datetime", 
                                   datetime_pm - 7200, pm_datetime_new),
         pm_datetime_new = if_else(next_steps == "Subtract 4 hours from datetime", 
                                   datetime_pm - 14400, pm_datetime_new),
         pm_datetime_new = if_else(next_steps == "Subtract 676 hours from datetime", 
                                   datetime_pm - 2433600, pm_datetime_new),
         pm_datetime_new = if_else(next_steps == "Subtract 7.75 hours from datetime", 
                                   datetime_pm - 27900, pm_datetime_new),
         pm_datetime_new = if_else(next_steps == "Subtract 78 hours from datetime", 
                                   datetime_pm - 280800, pm_datetime_new)) %>% 
  # filter(next_steps == "Subtract 78 hours from datetime")
  arrange(area, home, winter_id, sampling_visit, pm_datetime_new) %>% 
  ungroup()

# write_rds(elders_pm_new, paste0(file_path, "Output/elders_pm_clean.rds"))
```

>>>>

# Change function input to look at specific home
# Run these 4 lines together
pm_time_plot_function(location = "NPT", id = "163", visit = 2)
head(gaps, 10)
head(pm_desc, 10)
tail(pm_desc, 10)

@@

elders_pm_new <- elders_pm %>% 
  mutate(pm = if_else(pm > 12000, 999999, pm)) %>% 
  replace_with_na(replace = list(pm = 999999)) %>% 
  # join with file on data cleaning notes - refer to pm_sample_times_comparison file
  left_join(pm_sample_times_comparison, c("area", "home", "home_winter_id", "winter_id", "sampling_visit")) %>% 
  # filter out sampling visits with bad data - refer to pm_sample_times_comparison file
  filter(next_steps != "Do not use due to short run time") %>% 
  filter(next_steps != "Do not use due to high baseline/minimum values") %>% 
  filter(next_steps != "Do not use due to negatives") %>% 
  # replace PM < 1 (lower DustTrak limit) with 0.5 (lower limit / 2) 
  # only doing this for files with a few negative values
  mutate(pm = if_else(pm < 1, 0.5, pm)) %>% 
  # fix files with incorrect datetimes 
  mutate(datetime_pm = ymd_hms(datetime_pm),
         pm_datetime_new = if_else(next_steps == "Subtract 1 hour from datetime", 
                                   datetime_pm - 3600, datetime_pm),
         pm_datetime_new = if_else(next_steps == "Add 1 hour to datetime", 
                                   datetime_pm + 3600, pm_datetime_new),
         pm_datetime_new = if_else(next_steps == "Add 1 day to datetime", 
                                   datetime_pm + 86400, pm_datetime_new),
         pm_datetime_new = if_else(next_steps == "Add 2 hours to datetime", 
                                   datetime_pm + 7200, pm_datetime_new),
         pm_datetime_new = if_else(next_steps == "Add 174970 hours to datetime", 
                                   datetime_pm + 629892000, pm_datetime_new),
         pm_datetime_new = if_else(next_steps == "Subtract 2 hours from datetime", 
                                   datetime_pm - 7200, pm_datetime_new),
         pm_datetime_new = if_else(next_steps == "Subtract 4 hours from datetime", 
                                   datetime_pm - 14400, pm_datetime_new),
         pm_datetime_new = if_else(next_steps == "Subtract 676 hours from datetime", 
                                   datetime_pm - 2433600, pm_datetime_new),
         pm_datetime_new = if_else(next_steps == "Subtract 7.75 hours from datetime", 
                                   datetime_pm - 27900, pm_datetime_new),
         pm_datetime_new = if_else(next_steps == "Subtract 78 hours from datetime", 
                                   datetime_pm - 280800, pm_datetime_new)) %>% 
  # filter(next_steps == "Subtract 78 hours from datetime")
  arrange(area, home, winter_id, sampling_visit, pm_datetime_new) %>% 
  group_by(area, home, winter_id) %>% 
  mutate(pm_mean_winter = mean(pm, na.rm = TRUE)) %>% 
  group_by(area, home, winter_id, sampling_visit) %>% 
  mutate(pm_mean_visit = mean(pm, na.rm = TRUE)) %>%
  group_by(area, home, winter_id, sampling_visit, pm_sampling_day) %>% 
  mutate(pm_mean_daily = mean(pm, na.rm = TRUE),
         day_of_week = weekdays(pm_datetime_new)) %>%
  ungroup() %>% 
  mutate(sample_interval_days = pm_sample_interval) %>% 
  select(area, home, home_id_num, home_winter_id, winter_id, sampling_visit, 
         pm_sampling_day, pm_datetime_new, pm_sample_interval, pm, pm_mean_winter, 
         pm_mean_visit, pm_mean_daily, day_of_week, treatment, dtid, sample_obs,
         pm_comments) %>% 
  arrange(area, home, winter_id, sampling_visit, pm_datetime_new)

write_rds(elders_pm_new, paste0(file_path, "Output/elders_pm_clean.rds"))
```

### 2020-08-24 indoor_temp_rh_cleaning.Rmd
PM and RH cleaning/summary

---
title: "EldersAIR initial home/adult data work"
author: "Ethan Walker"
date: "Started 14 Feb 2020, Updated 14 Feb 2020"
output: pdf_document
---

@@

# Load, format, and save indoor temp/rh data for NP
```{r}
## Box location: Update Box location once final data loaded
np_temp_rh_initial <- read_csv("Input/NP/np_qtrack_20200214.csv") %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         rh_indoor_current = as.numeric(RelHumCur),
         rh_indoor_max = as.numeric(RelHumMax),
         rh_indoor_min = as.numeric(RelHumMin),
         temp_indoor_current = as.numeric(TempCCur),
         temp_indoor_max = as.numeric(TempCMax),
         temp_indoor_min = as.numeric(TempCMin),
         sampling_visit = as.factor(SamplingVisit),
         area = "NP") %>% 
  # replace -999 and 0 values with NA
  replace_with_na(replace = list(rh_indoor_current = -999, rh_indoor_max = -999,
                                 rh_indoor_min = -999, temp_indoor_current = -999,
                                 temp_indoor_max = -999, temp_indoor_min = -999)) %>% 
  replace_with_na(replace = list(rh_indoor_current = 0, rh_indoor_max = 0,
                                 rh_indoor_min = 0, temp_indoor_current = 0,
                                 temp_indoor_max = 0, temp_indoor_min = 0)) %>% 
  select(home_winter_id, area, rh_indoor_current, 
         rh_indoor_max, rh_indoor_min, temp_indoor_current, 
         temp_indoor_max, temp_indoor_min, sampling_visit) %>% 
  arrange(home_winter_id)
#write_rds(np_temp_rh_initial, "Output/np_temp_rh.rds")
```

# Load, format, and save indoor temp/rh data for NN
```{r}

```

# Join temp/rh data from different areas
```{r}
np_temp_rh <- read_rds("Output/np_temp_rh.rds")
nn_temp_rh <- read_rds("Output/nn_temp_rh.rds")
adult_indoor_temp_rh <- rbind(np_temp_rh, nn_temp_rh)
# write_rds(adult_indoor_temp_rh, "Output/adult_indoor_temp_rh.rds")
```

# Clean up all temp/rh data
```{r}
adult_indoor_temp_rh <- read_rds("Output/adult_indoor_temp_rh.rds")

kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")
indoor_temp_rh_clean <- kids_indoor_temp_rh %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id"))
# write_rds(indoor_temp_rh_clean, "Output/indoor_temp_rh_clean.rds")
```

>>>>

---
title: "EldersAIR initial temp/rh data work"
author: "Ethan Walker"
date: "Started 14 Feb 2020, Updated 24 Aug 2020"
output: pdf_document
---

@@

```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/EldersAIR/")
```

# Load, format, and save indoor temp/rh data
```{r}
## Box location: Update Box location once final data loaded
np_temp_rh_initial <- read_xlsx(paste0(file_path, "Input/NP/qtrack.xlsx"),
                                na = c("", "NULL")) %>% 
  # rename variables
  mutate(home_winter_id = factor(HomeWinterID),
         rh_indoor_current = as.numeric(RelHumCur),
         rh_indoor_max = as.numeric(RelHumMax),
         rh_indoor_min = as.numeric(RelHumMin),
         temp_indoor_current = as.numeric(TempCCur),
         temp_indoor_max = as.numeric(TempCMax),
         temp_indoor_min = as.numeric(TempCMin),
         sampling_visit = factor(SamplingVisit),
         area = "NPT") %>% 
  # replace -999 and 0 values with NA
  replace_with_na(replace = list(rh_indoor_current = -999, rh_indoor_max = -999,
                                 rh_indoor_min = -999, temp_indoor_current = -999,
                                 temp_indoor_max = -999, temp_indoor_min = -999)) %>% 
  replace_with_na(replace = list(rh_indoor_current = 0, rh_indoor_max = 0,
                                 rh_indoor_min = 0, temp_indoor_current = 0,
                                 temp_indoor_max = 0, temp_indoor_min = 0)) %>% 
  select(home_winter_id, area, 
         rh_indoor_max, rh_indoor_min, 
         temp_indoor_max, temp_indoor_min, sampling_visit) %>% 
  arrange(home_winter_id)

## Box location: Update Box location once final data loaded
nn_temp_rh_initial <- read_xlsx(paste0(file_path, "Input/NN/qtrack.xlsx"),
                                na = c("", "NULL")) %>% 
  # rename variables
  mutate(home_winter_id = factor(HomeWinterID),
         rh_indoor_current = as.numeric(RelHumCur),
         rh_indoor_max = as.numeric(RelHumMax),
         rh_indoor_min = as.numeric(RelHumMin),
         temp_indoor_current = as.numeric(TempCCur),
         temp_indoor_max = as.numeric(TempCMax),
         temp_indoor_min = as.numeric(TempCMin),
         sampling_visit = factor(SamplingVisit),
         area = "NN") %>% 
  # replace -999 and 0 values with NA
  replace_with_na(replace = list(rh_indoor_current = -999, rh_indoor_max = -999,
                                 rh_indoor_min = -999, temp_indoor_current = -999,
                                 temp_indoor_max = -999, temp_indoor_min = -999)) %>% 
  replace_with_na(replace = list(rh_indoor_current = 0, rh_indoor_max = 0,
                                 rh_indoor_min = 0, temp_indoor_current = 0,
                                 temp_indoor_max = 0, temp_indoor_min = 0)) %>% 
  select(home_winter_id, area, 
         rh_indoor_max, rh_indoor_min, 
         temp_indoor_max, temp_indoor_min, sampling_visit) %>% 
  arrange(home_winter_id)

# Combine locations and save
elders_temp_rh <- rbind(np_temp_rh_initial, nn_temp_rh_initial)

# write_rds(elders_temp_rh, paste0(file_path, "Output/elders_temp_rh.rds"))
```

# Clean up all temp/rh data
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/EldersAIR/")

elders_temp_rh <- read_rds(paste0(file_path, "Output/elders_temp_rh.rds"))

elders_ids_linked <- read_rds(paste0(file_path, "Output/elders_ids_linked.rds"))

elders_temp_rh_clean <- elders_temp_rh %>% 
  left_join(elders_ids_linked, by = c("area", "home_winter_id")) %>% 
  select(-adult_id_char, -adult_id_num) %>% 
  filter(!is.na(home_winter_id)) %>% 
  filter(!is.na(winter_id)) %>% 
  group_by(home, winter_id, sampling_visit) %>% 
  mutate(temp_indoor_max_new = if_else(temp_indoor_max < temp_indoor_min, 
                                       temp_indoor_min, temp_indoor_max),
         temp_indoor_min_new = if_else(temp_indoor_min > temp_indoor_max, 
                                       temp_indoor_max, temp_indoor_min),
         rh_indoor_max_new = if_else(rh_indoor_max < rh_indoor_min, 
                                     rh_indoor_min, rh_indoor_max),
         rh_indoor_min_new = if_else(rh_indoor_min > rh_indoor_max, 
                                     rh_indoor_max, rh_indoor_min)) %>% 
  ungroup() %>% 
  select(area, home, home_winter_id, home_id_num, winter_id, sampling_visit,
         treatment, temp_indoor_min_new, temp_indoor_max_new,
         rh_indoor_min_new, rh_indoor_max_new) %>% 
  rename(temp_indoor_max = temp_indoor_max_new,
         temp_indoor_min = temp_indoor_min_new,
         rh_indoor_max = rh_indoor_max_new,
         rh_indoor_min = rh_indoor_min_new) %>% 
  arrange(area, home, winter_id, sampling_visit)

summary(elders_temp_rh_clean)

# write_rds(elders_temp_rh_clean, paste0(file_path, "Output/elders_temp_rh_clean.rds"))

elders_temp_rh_clean <- read_rds(paste0(file_path, "Output/elders_temp_rh_clean.rds"))
```

### 2020-08-24 pm_summary_dustrak.Rmd
PM data cleaning
PM and RH cleaning/summary

---
title: "Elders PM Summary"
author: "Ethan Walker"
date: "Started 24 Feb 2020, Updated 23 July 2020"
output: pdf_document
---

@@

# Load data
elders_pm <- read_rds(paste0(file_path, "Output/elders_pm_clean.rds")) %>% 
  mutate(area = if_else(area == "NP", "NPT", area))
```

# Summary stats
```{r}
pm_summary <- elders_pm %>% 
  filter(winter_id == 1) %>% 
  #filter(pm < 500) %>% 
  mutate(pm = if_else(pm > 500, 500, pm)) %>% 
  group_by(area) %>% 
  summarize("n" = n(),
            "Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "25%" = quantile(pm, 0.25, na.rm = TRUE),
            "Median PM" = median(pm, na.rm = TRUE),
            "75%" = quantile(pm, 0.75, na.rm = TRUE),
            "Max PM" = max(pm, na.rm = TRUE),
            "Mean Sample Days" = mean(pm_sample_interval, na.rm = TRUE),
            "SD Sample Days" = sd(pm_sample_interval, na.rm = TRUE)) %>% 
  #select(-treatment) %>% 
  t() 
kable(pm_summary, digits = 1, align = "c")

@@

pm_by_month <- elders_pm %>% 
  filter(winter_id == 1) %>% 
  mutate(sampling_month = month(pm_datetime_new, abbr = TRUE)) %>%
  #filter(pm < 500) %>% 
  mutate(pm = if_else(pm > 500, 500, pm)) %>% 
  group_by(sampling_month) %>% 
  summarize("Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "25%" = quantile(pm, 0.25, na.rm = TRUE),
            "Median PM" = median(pm, na.rm = TRUE),
            "75%" = quantile(pm, 0.75, na.rm = TRUE),
            "Max PM" = max(pm, na.rm = TRUE))
pm_by_month

summary_stats <- elders_pm %>% 
  filter(winter_id == 1) %>% 
  group_by(area) %>% 
  distinct(home) %>% 
  summarize(n())
#summary_stats

summary_stats <- elders_pm %>% 
  filter(winter_id == 1) %>% 
  mutate(mean_threshold_25 = if_else(pm_mean >= 25, 1, 0),
         mean_threshold_25 = as.numeric(mean_threshold_25)) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  summarize(sum(mean_threshold_25)/n())
#summary_stats
```

# Boxplots for PM by study area
```{r}
boxplots_pm <- elders_pm %>% 
  filter(winter_id == 1) %>% 
  mutate(pm = if_else(pm > 500, 500, pm)) %>% 
  ggplot(aes(area, pm)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red",
                 position=position_nudge(x = -0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=mean, geom="text", 
                 size=7, position=position_nudge(x = -0.35, y = 0)) +
    stat_summary(fun.y=median, geom="point", shape=16, size=4, color="blue",
                 position=position_nudge(x = 0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=median, geom="text", 
                 size=7, position=position_nudge(x = 0.35, y = 0)) +
    theme_minimal() +
    #ylim(0, 250) +
    #geom_hline(yintercept = 50, color = "red", size = 1.2) +
    labs(y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    labs(title = "Area PM2.5, Winter 1", subtitle = "Mean = Red, Median = Blue") +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          title = element_text(size = 18, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_pm

boxplots_pm <- elders_pm %>% 
  filter(winter_id == 1) %>% 
  mutate(pm = if_else(pm > 500, 500, pm)) %>% 
  ggplot(aes(area, log(pm))) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red",
                 position=position_nudge(x = -0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=mean, geom="text", 
                 size=7, position=position_nudge(x = -0.35, y = 0)) +
    stat_summary(fun.y=median, geom="point", shape=16, size=4, color="blue",
                 position=position_nudge(x = 0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=median, geom="text", 
                 size=7, position=position_nudge(x = 0.35, y = 0)) +
    theme_minimal() +
    #ylim(0, 250) +
    #geom_hline(yintercept = 50, color = "red", size = 1.2) +
    labs(y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    labs(title = "Area PM2.5 (log transformed), Winter 1",
         subtitle = "Mean = Red, Median = Blue") +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          title = element_text(size = 18, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_pm
```

@@

```{r, fig.height=4, fig.width=4}
boxplots_elders_pm <- elders_pm %>% 
  filter(winter_id == 1) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  ggplot(aes(area, pm_mean)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red") +
    #scale_y_log10() +
    ylim(0, 200) +
    theme_minimal() +
    labs(y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black",
                                      margin = margin(t = 0, r = 0, b = 30, l = 0)),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_elders_pm

ggsave("boxplots_elders_pm.jpg", height = 7, width = 4)
```

```{r}
# homes that exceed PM guidelines
pm_guidelines <- elders_pm %>% 
  filter(winter_id == 1) %>% 
  group_by(home) %>% 
  mutate(pm_mean_winter = mean(pm_mean, na.rm = TRUE)) %>% 
  filter(pm_mean_winter > 35) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  group_by(area) %>% 
  count()
pm_guidelines
```

>>>>

---
title: "Elders PM Summary"
author: "Ethan Walker"
date: "Started 24 Feb 2020, Updated 24 Aug 2020"
output: pdf_document
---

@@

# Load data
elders_pm <- read_rds(paste0(file_path, "Output/elders_pm_clean.rds")) 
```

# Summary stats
```{r}
summary_stats <- elders_pm %>% 
  group_by(area, winter_id) %>% 
  distinct(area, home, winter_id, sampling_visit, .keep_all = TRUE) %>% 
  summarize("n" = n(),
            "Mean PM" = mean(pm_mean_winter, na.rm = TRUE), 
            "SD PM" = sd(pm_mean_winter, na.rm = TRUE),
            "Min PM" = min(pm_mean_winter, na.rm = TRUE), 
            "25%" = quantile(pm_mean_winter, 0.25, na.rm = TRUE),
            "Median PM" = median(pm_mean_winter, na.rm = TRUE),
            "75%" = quantile(pm_mean_winter, 0.75, na.rm = TRUE),
            "Max PM" = max(pm_mean_winter, na.rm = TRUE),
            "Mean Sample Days" = mean(pm_sample_interval, na.rm = TRUE),
            "SD Sample Days" = sd(pm_sample_interval, na.rm = TRUE)) %>% 
   t() 
kable(summary_stats, digits = 1, align = "c")

@@

pm_by_month <- elders_pm %>% 
  filter(winter_id == 1) %>% 
  mutate(sampling_month = month(pm_datetime_new, abbr = TRUE)) %>%
  #filter(pm < 500) %>% 
  mutate(pm = if_else(pm > 500, 500, pm)) %>% 
  group_by(sampling_month) %>% 
  summarize("Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "25%" = quantile(pm, 0.25, na.rm = TRUE),
            "Median PM" = median(pm, na.rm = TRUE),
            "75%" = quantile(pm, 0.75, na.rm = TRUE),
            "Max PM" = max(pm, na.rm = TRUE))
pm_by_month
```

@@

```{r, fig.height=6, fig.width=5}
boxplots_elders_pm <- elders_pm %>% 
  #filter(winter_id == 1) %>% 
  distinct(area, home, winter_id, .keep_all = TRUE) %>% 
  ggplot(aes(area, pm_mean_winter)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red") +
    #scale_y_log10() +
    #ylim(0, 200) +
    theme_minimal() +
    labs(y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black",
                                      margin = margin(t = 0, r = 0, b = 30, l = 0)),
          axis.text.y = element_text(size = 16, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(.~winter_id)
boxplots_elders_pm

# ggsave("boxplots_elders_pm.jpg", height = 7, width = 4)
```

```{r}
# homes that exceed PM guidelines
pm_guidelines <- elders_pm %>% 
  filter(winter_id == 1) %>% 
  filter(pm_mean_winter > 12) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  group_by(area) %>% 
  count()
pm_guidelines
```

```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/EldersAIR/")
elders_pm <- read_rds(paste0(file_path, "Output/elders_pm_clean.rds")) 
elders_temp_rh_clean <- read_rds(paste0(file_path, "Output/elders_temp_rh_clean.rds"))

# Summary data for results letters to send to participants
home_summary <- elders_pm %>% 
  left_join(elders_temp_rh_clean, by = c("area", "home", "winter_id", "sampling_visit")) %>% 
  filter(winter_id == 1) %>% 
  group_by(area, home) %>% 
  mutate("Min RH (%)" = round(mean(rh_indoor_min, na.rm = TRUE), digits = 0),
         "Max RH (%)" = round(mean(rh_indoor_max, na.rm = TRUE), digits = 0),
         "Mean PM2.5 (ug/m3)" = round(pm_mean_winter), digits = 0) %>% 
  distinct(area, home, .keep_all = TRUE) %>% 
  select(area, home, winter_id, "Mean PM2.5 (ug/m3)", "Min RH (%)", "Max RH (%)") %>%
  rename(Area = area,
         Home = home,
         Winter = winter_id) %>% 
  replace_with_na(replace = list("Min RH (%)" = "NaN")) %>% 
  replace_with_na(replace = list("Max RH (%)" = "NaN"))

write_csv(home_summary, paste0(file_path, "Output/elders_letter_data.csv"), na = "")
```
